\bf Model Visualization Techniques for a Social Network Model

### 2017-05-10 paper.Rnw
done with gof for now. move to making lineups

The \verbatim{plot.sienaGOF()} function allows us to visualize this fit. Below is an example of what the goodness-of-fit plot output looks like for indegree and outdegree statistics for a small model. Box plots and violin plots are drawn on top of each other in Figure~\ref{fig:sienagof} in order to show the distribution of the simulated network observations compared to the true data shown in red points connected by red lines. If the red points lie well within the simulated values, the model is a good fit to the data. The model examined in Figure~\ref{fig:sienagof} appears to do a better job of capturing the outdegree distribution than the indegree distrubtion of the data.

@@

\st{Because of the multi-level data structure of a network, viewing the model in the data space can depend on which aspect of the model you are interested in viewing. XXX Ideas: summary statistic dist. on nets simulated from model and show statistic from data; interactive plots showing objective function values on nodes; select node, select other node, show how the function values change interactively (future); XXX}

>>>>

The \verbatim{plot.sienaGOF()} function allows us to visualize this fit. Below is an example of what the goodness-of-fit plot output looks like for indegree and outdegree statistics for a small model. Box plots and violin plots are drawn on top of each other in Figure~\ref{fig:sienagof} in order to show the distribution of the simulated network observations compared to the true data shown in red points connected by red lines. If the red points lie well within the simulated values, the model is a good fit to the data. The model examined in Figure~\ref{fig:sienagof} appears to do a better job of capturing the outdegree distribution than the indegree distribution of the data.

@@

\st{Because of the multi-level data structure of a network, viewing the model in the data space can depend on which aspect of the model you are interested in viewing. XXX Ideas: summary statistic dist. on nets simulated from model and show statistic from data; interactive plots showing objective function values on nodes; select node, select other node, show how the function values change interactively (future); goodness of fit should do here. XXX}
